Flabby and injective objects in toposes

### 2022-02-16 paper-flabby-objects.tex
Better statement and better proof about Hom(T,I) (thanks to the anonymous reviewer)

\begin{prop}\label{prop:hom-flabby}
\begin{enumerate}
\item Let~$I$ be an injective set. Let~$T$ be an arbitrary set. Then the
set~$I^T$ of maps from~$T$ to~$I$ is flabby.
\item Let~$I$ be an injective~$R$-module. Let~$T$ be an arbitrary~$R$-module. Then the
set~$\Hom_R(T,I)$ of linear maps from~$T$ to~$I$ is flabby.
\end{enumerate}\end{prop}

\begin{proof}We first cover the case of sets. Let~$K \subseteq I^T$ be a
subterminal. We consider the injectivity diagram
\[ \xymatrix{
  T' \ar@{^{(}->}[r]\ar[d] & T \ar@{-->}@/^/[ld] \\
  I
} \]
where~$T'$ is the subset~$\{ s \in T \,|\, \text{$K$ is inhabited} \} \subseteq T$ and the
solid vertical map sends~$s \in T'$ to~$g(s)$, where~$g$ is an arbitrary element
of~$K$. This association is well-defined. Since~$I$ is injective, a dotted lift
as indicated exists. If~$K$ is inhabited, this lift is an element of~$K$.

The same kind of argument applies to the case of modules. If~$K$ is a
subterminal of~$\Hom_R(T,I)$, we define~$T'$ to be the submodule
$\{ s \in T \,|\, \text{$s = 0$ or $K$ is inhabited} \}$ and consider the
analogous injectivity diagram, where the solid vertical map~$f : T' \to I$ is now
defined by cases: Let~$s \in T'$. If~$s = 0$, then we set~$f(s) = 0$; if~$K$ is
inhabited, then we set~$f(s) \defeq g(s)$, where~$g$ is an arbitrary element
of~$K$. This association is again well-defined, and a dotted lift yields the
desired element of~$\Hom_R(T,I)$.
\end{proof}

Proposition~\ref{prop:hom-flabby} can be used to give an alternative proof of
Proposition~\ref{prop:injective-flabby} and to generalize
Proposition~\ref{prop:injective-flabby} to modules: If~$I$ is an injective set,
then the set~$I^1 \cong I$ is flabby. If~$I$ is an injective module, then the
set~$\Hom_R(R,I) \cong I$ is flabby.

>>>>

\begin{prop}\label{prop:hom-flabby}
\begin{enumerate}
\item Let~$I$ be an injective set. Let~$T$ be an arbitrary set. Then the
set~$I^T$ of maps from~$T$ to~$I$ is injective.
\item Let~$I$ be an injective~$R$-module. Let~$T$ be an arbitrary~$R$-module.
If~$T$ is flat, then the module~$\Hom_R(T,I)$ of linear maps from~$T$ to~$I$ is
injective. In the general case, it is at least flabby.
\end{enumerate}\end{prop}

\begin{proof}The first claim follows abstractly from the fact that the Hom
functor~$(\cdot)^T$ has a monomorphism-preserving left adjoint, namely the
product functor~$(\cdot) \times T$. Explicitly, an extension problem as in the
left half of the diagram
\[
  \xymatrix{
    A \ar@{^{(}->}[r]^i\ar[d]_f & B \ar@{-->}@/^/[ld]^{\overline{f}} \\
    I^T
  }
  \qquad
  \xymatrix{
    A \times T \ar@{^{(}->}[r]^{i \times T}\ar[d]_{g \defeq f^t} & B \times T \ar@{-->}@/^/[ld]^{\overline{g}} \\
    I
  }
\]
can be transposed to the extension problem as in the right half. A
solution~$\overline{g}$ gives rise to the solution~$\overline{f}$ of the
original problem by the setting~$\overline{f}(x) = (t \mapsto
\overline{g}(x,t))$.

The injectivity part of the second claim follows entirely analogously,
employing the tensor product instead of the cartesian product.

For the general statement, let~$K$ be a subterminal of~$\Hom_R(T,I)$. Let~$T'$
be the submodule $\{ s \in T \,|\, \text{$s = 0$ or $K$ is inhabited} \}
\subseteq T$ and let~$f : T' \to I$ be the linear map defined as follows:
Let~$s \in T'$. If~$s = 0$, then we set~$f(s) = 0$; if~$K$ is inhabited, then
we set~$f(s) \defeq g(s)$, where~$g$ is an arbitrary element of~$K$. This
association is well-defined. Since~$I$ is injective as a module, there is a
linear extension~$\overline{f} : T \to I$ of~$f$ along the inclusion~$T'
\subseteq T$. If~$K$ is inhabited, this extension is an element of~$K$ as
required.
\end{proof}

%Proposition~\ref{prop:hom-flabby} can be used to give an alternative proof of
%Proposition~\ref{prop:injective-flabby} and to generalize
%Proposition~\ref{prop:injective-flabby} to modules: If~$I$ is an injective set,
%then the set~$I^1 \cong I$ is flabby. If~$I$ is an injective module, then the
%set~$\Hom_R(R,I) \cong I$ is flabby.
